% Created 2022-06-04 Sat 16:14
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Bassam Saeed}
\date{\today}
\title{Emacs Configuration}
\hypersetup{
 pdfauthor={Bassam Saeed},
 pdftitle={Emacs Configuration},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.0.50 (Org mode 9.5.3)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Early Init}
\label{sec:org3e512f7}
Emacs 27+ loads \texttt{early-init.el} before initializing certain graphical
elements and the package manager. With this, we can speed up initial
start.
\subsection{Avoid GC at startup}
\label{sec:org580bf67}
Despite using Emacs as a daemon service (via Shepherd), it can be
useful to try to speed up startup as much as possible for those times
where I need to start it manually for whatever reason. This code is
taken from \href{https://github.com/doomemacs/doomemacs/blob/develop/docs/faq.org\#how-does-doom-start-up-so-quickly}{Doom Emac's excellent work with startup speed}.
\begin{verbatim}
(setq gc-cons-threshold most-positive-fixnum
      gc-cons-percentage 0.6)

;; Reset GC after init files are loaded
(add-hook 'emacs-startup-hook
	  (lambda ()
	    (setq gc-cons-threshold 16777216
		  gc-cons-percentage 0.1)))
\end{verbatim}

\subsection{Native Compilation Warning}
\label{sec:orged78b1e}
Silence native compilation warnings by the compiler. They are super
annoying when poping up as new windows.
\begin{verbatim}
(when (featurep 'native-compile)
  (setq native-comp-async-report-warnings-errors 'silent))
\end{verbatim}

\subsection{Clear out graphic elements}
\label{sec:org848c00d}
These are some of the default graphical elements that I don't need or
care for. I do keep the menu bar though. I find it useful for
discoverability of features.
\begin{verbatim}
(horizontal-scroll-bar-mode -1)
(tool-bar-mode -1)
(scroll-bar-mode -1)
\end{verbatim}

Likewise the splash page, while useful when I first started using
Emacs, is not needed for me anymore.
\begin{verbatim}
(setq inhibit-startup-message t)
\end{verbatim}

\subsection{Fonts}
\label{sec:org11ca543}
Setting the default fonts in the early-init file drastically speeds up
startup time. It can cut it almost by half in my testing compared to
having the code in \texttt{init.el}.
\begin{verbatim}
(set-face-attribute 'default nil :family "Iosevka" :height 150)
(set-face-attribute 'fixed-pitch nil :family "Iosevka")
(set-face-attribute 'variable-pitch nil :family "DejaVu Serif")
\end{verbatim}

\subsection{Disable default package manager}
\label{sec:org36e77af}
Since I don't use \texttt{package.el} (\texttt{guix} and \texttt{straight.el} instead) there's no
need for me to have this variable enabled. It probably doesn't hurt to
keep it since I don't install any packages via \texttt{package.el} but might as
well remove it.
\begin{verbatim}
(setq package-enable-at-startup nil)
\end{verbatim}
\end{document}